Improving Multi-Domain Neural Machine Translation with Differential Data Selection

### 2021-02-16 2021/acl-ijcnlp2021/mdmt.tex
local changes

\section{Results and discussion \label{sec:results}}
\begin{table*}
  \centering% \small
  \begin{adjustbox}{width=2\columnwidth,center}
  \begin{tabular}{|p{3.0cm}|*{13}{r|}} \hline
    \multirow{2}{*}{Training} & \multicolumn{6}{|c}{$\lambda^t_d$} & \multicolumn{6}{|c|}{BLEU} & \multirow{2}{*}{BLEU} \\ \cline{2-13}	
  mixture & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & average \\
    \hline
  \system{Mixed-$0.0$} & 0.166&0.166 &0.166 &0.166 &0.166 & 0.166 & 35.26 &54.09 &52.49& 31.86& 44.94& 89.54& 51.36\\
  \system{Mixed-$0.25$} & 0.166&0.166 &0.166 &0.166 &0.166 & 0.166 &35.92& 54.87& 52.55& 32.55& 44.98& 90.28& 51.86\\
  \system{Mixed-$0.5$} & 0.166&0.166 &0.166 &0.166 &0.166 & 0.166 &36.11& 55.37& 51.76& 33.52& 46.23& 89.99& 52.16\\
  \system{Mixed-$0.75$} & 0.166&0.166 &0.166 &0.166 &0.166 & 0.166 &36.53&	55.03& 51.15& 33.98& 44.28& 87.22& 51.365\\
  \system{Mixed-$1.0$} & 0.166&0.166 &0.166 &0.166 &0.166 & 0.166 &37.33& 54.56& 50.05& 33.47& 43.23& 77.51& 49.36\\
  \system{Multi-DDS} & 0.166&0.166 &0.166 &0.166 &0.166 & 0.166 & & & & & & & \\
  \system{Multi-DDS-v1} & 0.166&0.166 &0.166 &0.166 &0.166 & 0.166 & & & & & & & \\
  \hline
  \end{tabular}
  \end{adjustbox}
\end{table*}
\begin{table*}
  \centering% \small
  \begin{adjustbox}{width=2\columnwidth,center}
  \begin{tabular}{|p{2cm}|*{13}{r|}} \hline
    \multirow{2}{*}{Training} & \multicolumn{6}{|c}{$\lambda^t_d$} & \multicolumn{6}{|c|}{BLEU} & \multirow{2}{*}{BLEU} \\ \cline{2-13}	
  mixture & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & average \\
    \hline
  \system{FT-Full} & 1.0 &0.0 & 0.0 &0.0 &0.0 & 0.0 &35.26 &54.09 &52.49& 31.86& 44.94& 89.54& 51.36\\
  \system{Multi-DDS} & 1.0 &0.0 & 0.0 &0.0 &0.0 & 0.0 &35.26 &54.09 &52.49& 31.86& 44.94& 89.54& 51.36\\
  \system{FT-Full} & 0.0 &1.0 & 0.0 &0.0 &0.0 & 0.0 &35.92& 54.87& 52.55& 32.55& 44.98& 90.28& 51.86\\
  \system{Multi-DDS} & 0.0 &1.0 & 0.0 &0.0 &0.0 & 0.0 &35.92& 54.87& 52.55& 32.55& 44.98& 90.28& 51.86\\
  \system{FT-Full} & 0.0 &0.0 & 1.0 &0.0 &0.0 & 0.0 &36.11& 55.37& 51.76& 33.52& 46.23& 89.99& 52.16\\
  \system{Multi-DDS} & 0.0 &0.0 & 1.0 &0.0 &0.0 & 0.0 &36.11& 55.37& 51.76& 33.52& 46.23& 89.99& 52.16\\
  \system{FT-Full} & 0.0 &0.0 & 0.0 &1.0 &0.0 & 0.0 &36.53&	55.03& 51.15& 33.98& 44.28& 87.22& 51.365\\
  \system{Multi-DDS} & 0.0 &0.0 & 0.0 &1.0 &0.0 & 0.0 &36.53&	55.03& 51.15& 33.98& 44.28& 87.22& 51.365\\
  \system{FT-Full} & 0.0 &0.0 & 0.0 &0.0 &1.0 & 0.0 &37.33& 54.56& 50.05& 33.47& 43.23& 77.51& 49.36\\
  \system{Multi-DDS} & 0.0 &0.0 & 0.0 &0.0 &1.0 & 0.0 &37.33& 54.56& 50.05& 33.47& 43.23& 77.51& 49.36\\
  \system{FT-Full} & 0.0 &0.0 & 0.0 &0.0 &0.0 & 1.0 &37.33& 54.56& 50.05& 33.47& 43.23& 77.51& 49.36\\
  \system{Multi-DDS} & 0.0 &0.0 & 0.0 &0.0 &0.0 & 1.0 &37.33& 54.56& 50.05& 33.47& 43.23& 77.51& 49.36\\
  \hline
  \end{tabular}
  \end{adjustbox}
  \label{tab:redomains}
\end{table*}
\section{Related Work \label{sec:related}}
\cite{Wang17instance} uses dynamic weighting (for sentences and domains) for DA.

>>>>

\section{Results and discussion \label{sec:results}}
\begin{table*}
  \centering% \small
  \begin{adjustbox}{width=2\columnwidth,center}
  \begin{tabular}{|p{3.0cm}|*{13}{r|}} \hline
    \multirow{2}{*}{Training} & \multicolumn{6}{|c}{$\lambda^t_d$} & \multicolumn{6}{|c|}{BLEU} & \multirow{2}{*}{BLEU} \\ \cline{2-13}	
  mixture & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & average \\
    \hline
  \system{Mixed-$0.0$} & 0.166&0.166 &0.166 &0.166 &0.166 & 0.166 & 35.26 &54.09 &52.49& 31.86& 44.94& 89.54& 51.36\\
  \system{Mixed-$0.25$} & 0.166&0.166 &0.166 &0.166 &0.166 & 0.166 &35.92& 54.87& 52.55& 32.55& 44.98& 90.28& 51.86\\
  \system{Mixed-$0.5$} & 0.166&0.166 &0.166 &0.166 &0.166 & 0.166 &36.11& 55.37& 51.76& 33.52& 46.23& 89.99& 52.16\\
  \system{Mixed-$0.75$} & 0.166&0.166 &0.166 &0.166 &0.166 & 0.166 &36.53&	55.03& 51.15& 33.98& 44.28& 87.22& 51.365\\
  \system{Mixed-$1.0$} & 0.166&0.166 &0.166 &0.166 &0.166 & 0.166 &37.33& 54.56& 50.05& 33.47& 43.23& 77.51& 49.36\\
  \system{Multi-DDS} & 0.166&0.166 &0.166 &0.166 &0.166 & 0.166 & 37.26 & 55.07&50.96&33.49&43.41&90.76& 51.83 \\
  \system{Multi-DDS-v1} & 0.166&0.166 &0.166 &0.166 &0.166 & 0.166 & 36.96 & 55.55 & 52.88 & 33.06 & 44.52 &91.25 & 52.37\\
  \hline
  \end{tabular}
  \end{adjustbox}
\end{table*}
\begin{table*}
  \centering% \small
  \begin{adjustbox}{width=2\columnwidth,center}
  \begin{tabular}{|p{2cm}|*{13}{r|}} \hline
    \multirow{2}{*}{Training} & \multicolumn{6}{|c}{$\lambda^t_d$} & \multicolumn{6}{|c|}{BLEU} & \multirow{2}{*}{BLEU} \\ \cline{2-13}	
  mixture & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & average \\
    \hline
  \system{FT-Full} & 1.0 &0.0 & 0.0 &0.0 &0.0 & 0.0 &37.45&51.26&45.47&31.62&37.55&65.22& \\
  \system{FT-Res} & 1.0 &0.0 & 0.0 &0.0 &0.0 & 0.0 &35.26 &54.09 &52.49& 31.86& 44.94& 89.54& 51.36\\
  \system{Multi-DDS} & 1.0 &0.0 & 0.0 &0.0 &0.0 & 0.0 &35.26 &54.09 &52.49& 31.86& 44.94& 89.54& 51.36\\
  \system{FT-Full} & 0.0 &1.0 & 0.0 &0.0 &0.0 & 0.0 &35.92& 54.87& 52.55& 32.55& 44.98& 90.28& 51.86\\
  \system{FT-Full} & 1.0 &0.0 & 0.0 &0.0 &0.0 & 0.0 &35.26 &54.09 &52.49& 31.86& 44.94& 89.54& 51.36\\
  \system{Multi-DDS} & 0.0 &1.0 & 0.0 &0.0 &0.0 & 0.0 &35.92& 54.87& 52.55& 32.55& 44.98& 90.28& 51.86\\
  \system{FT-Full} & 0.0 &0.0 & 1.0 &0.0 &0.0 & 0.0 &36.11& 55.37& 51.76& 33.52& 46.23& 89.99& 52.16\\
  \system{FT-Full} & 1.0 &0.0 & 0.0 &0.0 &0.0 & 0.0 &35.26 &54.09 &52.49& 31.86& 44.94& 89.54& 51.36\\
  \system{Multi-DDS} & 0.0 &0.0 & 1.0 &0.0 &0.0 & 0.0 &36.11& 55.37& 51.76& 33.52& 46.23& 89.99& 52.16\\
  \system{FT-Full} & 0.0 &0.0 & 0.0 &1.0 &0.0 & 0.0 &36.53&	55.03& 51.15& 33.98& 44.28& 87.22& 51.365\\
  \system{FT-Full} & 1.0 &0.0 & 0.0 &0.0 &0.0 & 0.0 &35.26 &54.09 &52.49& 31.86& 44.94& 89.54& 51.36\\
  \system{Multi-DDS} & 0.0 &0.0 & 0.0 &1.0 &0.0 & 0.0 &36.53&	55.03& 51.15& 33.98& 44.28& 87.22& 51.365\\
  \system{FT-Full} & 0.0 &0.0 & 0.0 &0.0 &1.0 & 0.0 &37.33& 54.56& 50.05& 33.47& 43.23& 77.51& 49.36\\
  \system{FT-Full} & 1.0 &0.0 & 0.0 &0.0 &0.0 & 0.0 &35.26 &54.09 &52.49& 31.86& 44.94& 89.54& 51.36\\
  \system{Multi-DDS} & 0.0 &0.0 & 0.0 &0.0 &1.0 & 0.0 &37.33& 54.56& 50.05& 33.47& 43.23& 77.51& 49.36\\
  \system{FT-Full} & 0.0 &0.0 & 0.0 &0.0 &0.0 & 1.0 &37.33& 54.56& 50.05& 33.47& 43.23& 77.51& 49.36\\
  \system{FT-Full} & 1.0 &0.0 & 0.0 &0.0 &0.0 & 0.0 &35.26 &54.09 &52.49& 31.86& 44.94& 89.54& 51.36\\
  \system{Multi-DDS} & 0.0 &0.0 & 0.0 &0.0 &0.0 & 1.0 &37.33& 54.56& 50.05& 33.47& 43.23& 77.51& 49.36\\
  \hline
  \end{tabular}
  \end{adjustbox}
  \label{tab:redomains}
\end{table*}
\section{Related Work \label{sec:related}}
\cite{Wang17instance} uses dynamic weighting (for sentences and domains) for DA.
